Most common replacements performed by programmers when fixing bugs

### 2016-02-09 MSRChallenge2016.tex
Changed most of the info in the file
I put my paper there, feel free to edit all of it to include and remove
parts of it as you think it works best. I will remove the unimportant
parts of my contributions

\documentclass{sig-alternate-05-2015}

@@

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Alternate {\ttlit ACM} SIG PrTeX
Format\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawredfe P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file. A compiled PDF version
is available on the web page to help you with the
`look and feel'.
\end{abstract}

@@

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

@@

\keywords{ACM proceedings; \LaTeX; text tagging}

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning,
clark:pct, braams:babel, herlihy:methodology},
conference proceedings \cite{clark:pct} or
books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed or supported.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps} files to be
displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
\textbf{.pdf} format.  Note that most modern \TeX\ system will convert
\textbf{.eps} to \textbf{.pdf} for you on the fly.  More details on
each of these is found in the \textit{Author's Guide}.

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.
and don't forget to end the environment with
{figure*}, not {figure}!

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

>>>>

\documentclass{sig-alternate-05-2015}
\usepackage{graphicx}
\graphicspath{ {} }

@@

%Conference
%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

%\acmPrice{\$0.00}

%
% --- Author Metadata here ---
\conferenceinfo{MSR}{2016 Austin, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Most common replacements performed by programmers when fixing bugs}

%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Mauricio Soto\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{mauriciosoto@cmu.edu}
% 2nd. author
\alignauthor Chu Pan Wong   
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}       
\and  % use '\and' if you need 'another row' of author names
% 3rd. author
\alignauthor Ferdinand Lastname
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}
% 4th. author
\alignauthor
Claire Le Goues\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{clegoues@cs.cmu.edu}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{February 2, 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
\textbf{
With the rise of automated program repair in the last couple of years, there are a lot of questions to remain unanswered. We performed a study on the Github dump of September 2015 in which we analyzed all the fixing revisions of this dataset, and found all the replacements made in these 46,301,429 files from real life projects in Github.
}

\textbf{
We found very valuable information to guide automatic software repair, such as the most common and least common replacements made by human developers in order to build a successful patch; we analyzed the most and least common statement to replace others, and the most and least likely statement to get replaced by other. We also analyzed, once you have a statement that you want to replace (a faulty statement), what are the most likely statements to replace it for. These information will help automatic program repair tools to be more maintainable and user friendly, taking it one step closer to what humans developers do to repair their code.
}

\end{abstract}

@@

@@

\keywords{Automatic error repair; Maintainability; Human-like patches}

\section{Introduction}
Automatic bug repair is the branch of computer science that deals with automated ways to repair errors in software. There have been several approaches taken towards improving the different methodologies to repair bugs in software automatically \cite{dongsun}\cite{weimer}\cite{claire} \cite{kai}, one of the most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, which is an evolutionary program repair tool and applies four different kinds of possible changes to code in order to find a patch for a given bug. These changes are the following: Delete, Replace, Swap and Append.

Our research aims to provide guidelines to improve three out of four of these possible changes: Delete, Replace and Append. It will provide the data necessary for this tool and other approaches to have a guide on what is the way in which human programmers change their code when coding a fix for a bug. This way it will make it more likely for automatic error repair approaches to succeed in finding a patch for a particular error, and also, to provide automatic error repair software with heuristics to make the patches more human-like and therefore more readable and maintainable by human developers.

In this article we study the frequency with which human programmers replace, delete and append different statements to their source code in order to fix a bug.

\section{Methodology}
Our methodology is applied to the latest official data dump of Github as of September 2015 provided by \cite{robert}.

\subsection{Statements}
Statements are the building blocks of software. There are several kinds of statements in which software can be divided into. In our approach we are trying to find patterns in the way human programmers replace, delete or append statements in order to fix a bug in their code.

The definitions of statements vary slightly depending on the programming language being used, but regardless of this, the vast majority of statements classifications are very similar independent of the language used. For our study we took a very standard classification of statements provided by the Java Development Tools package.

In this classification we have twenty two kinds of statements, from which we took fifteen of them for the gathering and analysis of our data. The list of statements taken for our analysis is the following:

\begin{verbatim}
AssertStatement
BreakStatement
ContinueStatement 
DoStatement 
ForStatement 
IfStatement 
LabeledStatement
ReturnStatement 
SwitchCase 
SwitchStatement 
SynchronizedStatement
ThrowStatement 
TryStatement 
TypeDeclarationStatement
WhileStatement
\end{verbatim}

The remaining six kinds of statements were not considered to be part of our analysis for three main reasons. We will start with this following statement type:

\begin{verbatim}
Block
\end{verbatim}

The statement type known as "Block" was not included since our main goal is to provide guidelines to automatic bug repair software to be able to create patches in a more guided way. It is irrelevant for an automatic bug repair software to know that an statement was replaced by a "Block", since a Block is an unknown amount of statements concatenated together and knowing that there is an infinite amount of possible permutations of statements that can be a Block, makes it useless to know that an statement was replaced by a Block, since a Block can be basically any possible combination of statements.

The next statement type:
\begin{verbatim}
EmptyStatement 
\end{verbatim}

The statement known as "EmptyStatement" is an statement that doesn't perform any action. Therefore, replacing any statement for an empty statement is equivalent to deleting that statement, and that case is treated separately.

The third reason of why the remaining five statement types were not included in the analysis is because these statement types are not supported by Boa as a StatementKind to the best of our knowledge. The remaining five statement types are the following:

\begin{verbatim}
ConstructorInvocation
EnhancedForStatement
ExpressionStatement
SuperConstructorInvocation
VariableDeclarationStatement
\end{verbatim}

We focused on the initial list of fifteen statement kinds mentioned at the beginning of the section.

\begin{table*}
\centering
\caption{Amount of appearances per replace kind}
\resizebox{\textwidth}{100pt}{
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
 &Assert&Break&Continue&Do& For&If&Label&Return&Switch&Switch& Synchronized&Throw&Try&TypeDecl&While
\\ \hline
\texttt{Assert}	&-&340&	232	&27	&517	&1764&	14&	1260	&211	&191&	82&	1004	&352	&0	&206
\\ \hline
\texttt{Break} &455	&-&	1254&	176	&3757	&9096&	90&	10538&	771	&455&	672	&3123&	3660&	18&	2278
 \\ \hline
\texttt{Continue} & 229	&1384	&-&	221	&1909	&3094&	85&	3486	&772&	635	&233&	1227&	1493&	30&	1086
 \\   \hline
\texttt{Do} &32	&205&	171	&-&	474	&648	&12&	543	&106	&92&	44	&227	&325&	4&	558
  \\ \hline
\texttt{For} &505	&3366	&1516	&316	&-&	14547	&56	&14924	&2791	&1852	&1044&	5642&	5796	&41	&6582
 \\ \hline
\texttt{If}& 1402&	8820&	2430&	476	&13703&-&		247	&30489	&8639	&5710	&2472&	8960&	13714&	84&	5622
 \\ \hline
\texttt{Label} &19&	44	&46	&6&	56	&255	&-&	270	&44	&22	&5	&80&	53&	2	&33
\\ \hline
\texttt{Return} &1219&	8603	&3009	&531	&12620	&28536&	164	&-&	6088&	3657&	2021&	15346&	11486&	71	&4684
 \\ \hline
\texttt{Case} &298	&839&	506	&125&	3002&	8039&	33&	6261	&-&	126	&649&	2206&	2784&	24&	1864
\\ \hline
\texttt{Switch}&281	&533&	379	&56	&1997	&5175&	22	&4090&	126	&-&	212	&1571	&1311	&7&	878
 \\ \hline
\texttt{Synchronized} &79&	606&	289&	66	&1122&	3070&	158&	2853	&562&	256	&-&	1303&	1274&	8	&466
 \\ \hline
\texttt{Throw} &821&	2844&	1195	&197&	5993	&10664&	113&	16688&	2002	&1446&	936		&-&4443&	37&	1934
 \\ \hline
\texttt{Try}& 440&	3976&	1254&	214	&6414&	16294&	45	&14119	&3178	&1509	&1243&	4795	&-&	46&	2218
 \\ \hline
\texttt{TypeDecl} &2&	35&	15	&1&	49	&83&	1&	137	&21&	9&	4&	35&	46	&-&	11
 \\ \hline
\texttt{While}& 301&	2295&	1016&	937	&8257&	6587&	41	&6280&	1866&	766	&606&	2028&	2677&	27	&-
 \\ \hline
\end{tabular}
}
\end{table*}

\subsection{Data Collection}
We used the Boa platform \cite{robert} to be able to query the Github repository looking for patterns that humans use to patch errors in the their code. Our main goal is to provide automatic error fixing approaches with the data necessary to be able to replace, delete and append statements in the patches being created by them.

Our Boa queries are divided in two types:

\subsubsection{Replace Query}
The replace query is a query in which first we set the project that we are going to use, which is the Github dump of September 2015 provided by \cite{robert}.

We then create a visitor to traverse all the nodes of this repository. First thing the visitor does is to ask weather the node is a Revision, and if it is, then it asks if it is a fixing revision. Therefore we are analyzing only files that were already committed and are now being reviewed to fix an error. We use Boa's infrastructure to do this by visiting the node they label as "Revision" and then calling the function defined by Boa "isfixingrevision()".

A replacement needs two statements, one that is deleted and another one that is inserted.
We then go through all the files that have been changed in this data set asking for two conditions: it must be a fixing revision and there must have been a previous version of this file before. If these conditions are met then we initialize two counters: one for the first statement we are analyzing (the one that was deleted), and another one for the second statement we are analyzing (the one that was inserted).

At this point we visit each statement in the previous state of that changed file, before the change was applied and we count the amount of appearances of the first statement we are analyzing (the one that was deleted), and then we count the amount of appearances of the second statement we are analyzing (the one that was inserted). We save these values, and do the same for the latest version of the file and save these values as well.

We then compare these results to see if either the first and second statements being analyzed increased or decreased. Depending on these we have two conditionals:

If the amount of occurrences of the first statement decreased and the amount of occurrences  of the second statement increased on the same file, then we say that the first statement was replaced by the second statement in that file. Likewise, if the amount of occurrences of the first statement increased and the amount of occurrences  of the second statement decreased on the same file, we say that the second statement was replaced by the first statement in that file. We count the amount of files in which this happens for each of these two cases.

We need to test this with all the possible combinations of two different statement types since we want to know what is the probability of an specific statement to be replaced by another specific statement. For example, we want to know how often does a For loop gets replaced by a While loop in a successful human written patch, or how often does a Break statement gets replaced by a Continue statement in a successful human written patch.

Because of this we have created Table 1 which records the amount of replaces happening from one kind of statement to another. It is a matrix of fifteen by fifteen slots that describes which statements are being replaced by which other.

The numbers in the slots represent the amount of files in which that replacement took place. In the first column we have the list of statements that are being replaced, and on the top row we have the list of statements for which that statement was replaced for. For example, if we take the intersection of row 5 (DoStatement row) and column 2 (AsserStatement column), we have a 32, which means that from the 46,301,429 files categorized by Boa as fixing revisions in Github in the month of September 2015, only 32 of them replaced a DoStatement for an AssertStatement.

It is important to notice  that this analysis doesn't consider replacing an statement kind for a different version of the statement kind, since it is counting the amount of appearances of each statement kind. So, if for example, the developer modifies the condition inside of an if statement, the amount of if statements in the file is going to remain the same

\subsubsection{Delete/Append Query}

The Delete/Append Query is similar to the Replace Query with some variations to count for the amount of times that a file was changed and a particular statement kind was either deleted or append, and the rest of the statement kinds remained the same.

We created a Boa file in which first we create an output variable to count all the amount of files in which a statement kind was deleted or appended. Similar to the previous query, we visit all the files labeled as fixing revisions, then visit every node of the previous version of the revision, counting the amount of statement kinds of each one of the possible fifteen different ones. We then do the same for the later version of the revision, counting the different statement kinds.

Finally, we compare the amounts of the previous version, with the new version. For each of the revisions, we ask if the amount of statements stays the same for all the statement kinds, except for X kind of statement. When the amount of statements is different in the previous version than the latest version for X kind of statement. Then we ask if X kinds of statement is greater in the previous version or the latest version. If the amount of appearances of X kind of statement is greater in the previous version than the latest version, and all the remaining fourteen statement kinds have the same amount in the previous than the latest version, then we say that one or more of the statements of kind X were deleted. Otherwise, if the latest version has a greater amount of appearances of X kind of statement and the rest have the same amount of appearances in both the previous and the latest version, then we say that one or more statements of kind X were appended or added to the fixing revision.

%\begin{table}
%\centering
%\caption{Amount of appearances of replaces}
%\begin{tabular}{ | c | c | c | }\hline
% &Deleted&Appended
%\\ \hline
%\texttt{Assert} & &\\ \hline
%\texttt{Break} &   & \\ \hline
%\texttt{Continue} & & \\   \hline
%\texttt{Do} & &  \\ \hline
%\texttt{For} & & \\ \hline
%\texttt{If} &  &  \\ \hline
%\texttt{Label} & & \\ \hline
%\texttt{Return} &  & \\ \hline
%\texttt{Case} &  & \\ \hline
%\texttt{Switch} &  & \\ \hline
%\texttt{Synchronized} & & \\ \hline
%\texttt{Throw} &  &\\ \hline
%\texttt{Try} &   & \\ \hline
%\texttt{TypeDecl} &&    \\ \hline
%\texttt{While} &   &   \\ \hline
%\end{tabular}
%\end{table}

\subsection{Data Analysis}
Our queries were ran on the dump of Github of September 2015. In these real life projects we found 46,301,429 files being fixed. In these files, there is a total of 517,281 statement kinds being replaced, and 511,198 replacing these statements kinds.

We analyzed each of these files looking for statement kinds being either replaced by other kinds, deleted or appended to the file.

We found that the most common Replacer statement kind, meaning the statement kind that most commonly replaces others is the \textbf{If Statement} with 101,366 appearances. The least common Replacer, meaning the statement kind which is less likely to replace other statement kinds is the \textbf{Type Declaration Statement} with 447 appearances.

The most common Replacee, which is the most likely statement kind to be replaced by another statement kind is the \textbf{Return Statement} with 111,938 appearances. The least common Replacee, which is the least common statement to be replaced by another statement kind is the \textbf{Type Declaration Statement} with 399 appearances.

\subsubsection{Likeliness of replacement}
This study is directly applicable to automatic software repair. Most common tools for automatic software repair \cite{dongsun}\cite{weimer}\cite{claire} first find a faulty statement using several different fault localization techniques \cite{zach}, and once they have that faulty statement, they apply different kinds of edits to it, usually at random. Which makes it equally likely to replace an statement for another without looking at the kinds of statements being replaced.

With this study, we are able to make a more accurate guess, when having a known faulty statement, to which statement it is more likely to replace it for. By performing simple math with the data of Table 1, we can find the most likely replacements that will end up being a successful patch.

For example, if we have a faulty statement that happens to be a For Statement. Then we can look up in Table 1 the For Statement Column (6th column). If we add all the values in that column, we get 59,870 changes in which a For Statement was replaced by some other kind of statement. Then we calculate the percentage of each of the values in the column to see the likeliness of each of the statements to replace it for, and in this example we see that the top 3 most likely statements to replace a For Statement are an If statement with a 22.88\% likeliness, followed by a return statement with a 21.08\%, and third is a While statement with a 13.73\% of likeliness to replace a For Statement.
